\documentclass[11pt]{article}

\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor = black
}
\usepackage[
    left = 0.25in, 
    right = 0.25in, 
    top = 0.25in, 
    bottom = 0.25in
]{geometry}
\usepackage{enumitem}
\setlist[itemize]{
    topsep = 0.1em, 
    itemsep = 0.0em, 
    parsep = 0.0em, 
}
\usepackage{titlesec}
\titlespacing*{\section}{0em}{0.2em}{0em}
\usepackage{changepage}

\pdfgentounicode=1 

\begin{document}

    \pagestyle{empty}

    \begin{center}
        \textbf{\LARGE Nathan Au}\\[0.4em]
        Montr\'{e}al, QC, Canada 
        $\bullet$
        \href{im.nathanau@gmail.com}{\underline{im.nathanau@gmail.com}} 
        $\bullet$ 
        \href{https://nathan-au.github.io}{\underline{nathan-au.github.io}}
        $\bullet$ 
        \href{https://www.linkedin.com/in/-nathanau}{\underline{/in/-nathanau}}
    \end{center}

    \vspace{-1.0em}

    \section*{\large Education}
    \hrule 
    \vspace{0.4em}
    \begin{adjustwidth}{0.125in}{0in}
        \textbf{Concordia University} \hfill \textbf{Montr\'{e}al, QC}\\
        Bachelor of Engineering -- Software Engineering, Co-op \hfill Sep. 2024 -- May 2028 (expected)
        \begin{itemize}
            \item GPA: 3.4/4.0
        \end{itemize}
    \end{adjustwidth}

    \section*{\large Experience}
    \hrule 
    \vspace{0.4em}
    \begin{adjustwidth}{0.125in}{0in}
        \textbf{Software Developer -- Mobile \& AI Integration} \hfill \textbf{Nov. 2024 -- Apr. 2025}\\
        Google Developer Group -- Concordia University \hfill Hybrid / Montr\'{e}al, QC
        \begin{itemize}
            \item Developed a cross-platform Flutter mobile application that helps university students in Montr\'{e}al connect with peers, discover local study spots, and stay up to date on upcoming campus events all on one platform. 
            \item Built a data-driven recommendation engine using user profiles managed in Firebase Realtime Database and Gemini LLM integration via Vertex AI to generate personalized connection suggestions based on shared interests and goals.
            \item Integrated the Concordia University Open Data API to retrieve 60+ upcoming campus events in real-time and implemented responsive geolocation-based features using flutter\_map for interactive study spot discovery.
            \item Delivered technical presentations at Flutter Montr\'{e}al and Concordia University to audiences of 100+ attendees and produced the official launch video to showcase system architecture and data flow.
        \end{itemize}
        \textbf{Systems Engineering Intern -- Hardware \& Operations} \hfill \textbf{Sep. 2023 -- Feb. 2024}\\
        Renaissance Network Reinvent \hfill Ottawa, ON
        \begin{itemize}
            \item Performed system-level testing on satellite tracking units in FlightTest diagnostic software to ensure pre-deployment hardware-software sync and debugged 200+ electronic modules by validating I/O with test instrumentation.
            \item Reduced material costs and improved repair efficiency by salvaging $\sim$100 high-value microchips and electronic components from scrap PCBs through component-level desoldering to enable parts reuse in future repairs.
            \item Managed inventory of 1,000+ repair components using barcode-enabled data capture and Excel-driven tracking (PivotTables, XLOOKUP) to validate records and maintain data accuracy across repair logistics pipelines.
            \item Executed end-to-end operational workflows (test, debug, repair, assembly, quality control) in collaboration with multiple cross-functional engineering teams to meet production deadlines.
        \end{itemize}
    \end{adjustwidth}

    \section*{\large Projects}
    \hrule 
    \vspace{0.4em}
    \begin{adjustwidth}{0.125in}{0in}
        \textbf{Reel Digest} $\vert$ Python, Telegram Bot API, Ollama (Granite 4), SQLite, yt-dlp, OpenCV $\vert$ \href{https://github.com/nathan-au/reel-digest}{\underline{Source Code}} \hfill \textbf{Dec. 2025}\\
        Messaging-based productivity tool that saves users' time by turning short-form content into concise text summaries.
        \begin{itemize}
            \item Designed a multi-modal media processing pipeline with Google STT for audio transcription and OpenCV computer vision/Tesseract OCR optical character recognition for on-screen text extraction to enable contextual LLM analysis.
            \item Configured a SQLite caching layer to eliminate redundant inference, persist user history, and successfully serve live summaries for 300+ unique production requests.
        \end{itemize}
        \textbf{TeeFour AI} $\vert$ Python, FastAPI, Ollama (Gemma 3), SQLModel, Tesseract OCR, pytest $\vert$ \href{https://github.com/nathan-au/teefour-ai}{\underline{Source Code}} \hfill \textbf{Oct. 2025}\\
        Automated tax document processing system that eliminates manual data entry for tax accounting workflows.
        \begin{itemize}
            \item Engineered a two-layer document classification algorithm using PyMuPDF/Tesseract OCR to categorize known document types (T4s, IDs, receipts) via filename analysis and content-keyword matching logic.
            \item Streamlined tax form data field extraction by integrating a locally hosted LLM to transform unstructured OCR text inputs into validated, machine-readable JSON outputs for downstream use in tax filing software.
        \end{itemize}
        \textbf{PartCart} $\vert$ Vue.js, Supabase, Tailwind CSS, Vite, JavaScript $\vert$ \href{https://github.com/nathan-au/part-cart}{\underline{Source Code}} \hfill \textbf{May 2025}\\
        Internal communication platform that simplifies the part procurement process for computer repair operations.
        \begin{itemize}
            \item Architected a full-stack order management system using Vue.js and Supabase with role-based access control to support real-time communication between technicians (requesting) and buyers (approving/denying).
            \item Constructed reactive dashboard interfaces with Supabase Realtime and Tailwind CSS to incorporate live order updates, form validation logic, order list sorting/filtering, priority-based colour indicators, and order detail modals.
        \end{itemize}
        \textbf{More projects: \href{https://nathan-au.github.io/\#projects}{\underline{nathan-au.github.io}}}
    \end{adjustwidth}

    \section*{\large Relevant Skills}
    \hrule 
    \vspace{0.4em}
    \begin{adjustwidth}{0.125in}{0in}
        \textbf{Technical Languages}: Python, TypeScript, JavaScript, SQL, Dart, HTML, CSS, C++, Java\\
        \textbf{Frameworks \& Libraries}: FastAPI, Flutter, Vue.js, Next.js, Tailwind CSS, Pandas, Matplotlib, NumPy, pytest, Hugging Face Transformers, PyTorch \\
        \textbf{Practices}: OOP, REST APIs, Agile/Scrum, Git Version Control, Unit \& E2E Testing, ETL Pipelines, LLMs, NLP\\
        \textbf{Spoken Languages}: English (Native), French (Professional -- CECR DELF B2)
    \end{adjustwidth}
\end{document}